Predicting Bike Usage at UofT St. George with Bayesian Poisson Regression

### 2024-12-01 paper/paper.qmd
The code includes comments regarding the usage of LLM
The code includes comments regarding the usage of LLM
figure lable updated
figure lable updated

@@

```{r, fig.pos="H", fig.width=8, fig.height=6}
#| label: fig-result
#| fig-cap: "The actual count from 4:00 AM to 8:00 AM on September 26, 2024 vs the predicted count for the same time interval in 2025."
#| echo: false
#| message: false
#| warning: false

@@

# Create the plot
ggplot(data_long, aes(x = station_name, y = value, fill = Note)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.7), width = 0.7) +
  geom_text(aes(label = value), 
            position = position_dodge(width = 0.7), 
            vjust = -0.5, 
            size = 3) + 
  labs(
    x = "Station Name",
    y = "Usage",
  ) +
  scale_fill_manual(
    values = c("count" = "pink", "prediction" = "skyblue"),
    labels = c("count" = "Actual count in 2024", "prediction" = "Predicted count in 2025") 
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

>>>>

Additionally, this project utilized OpenAI's ChatGPT-4 [@openai2024chatgpt] to assist in writing parts of the code.

@@

```{r, fig.pos="H", fig.width=8, fig.height=6}
#| label: fig-result
#| fig-cap: "The actual usage from 4:00 AM to 8:00 AM on September 26, 2024 vs the predicted usage for the same time interval in 2025."
#| echo: false
#| message: false
#| warning: false

@@

# Create the plot
ggplot(data_long, aes(x = station_name, y = value, fill = Note)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.7), width = 0.7) +
  geom_text(aes(label = value), 
            position = position_dodge(width = 0.7), 
            vjust = -0.5, 
            size = 3) + 
  labs(
    x = "Station Name",
    y = "Usage",
  ) +
  scale_fill_manual(
    values = c("count" = "pink", "prediction" = "skyblue"),
    labels = c("count" = "Actual usage in 2024", "prediction" = "Predicted usage in 2025") 
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
